---
title: "Staging Shift Schedule for GPC Ci305"
author: "Shuai Wang & Aaron Makubuya"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem statement
The staging/unstaging work is done by dedicated personnel.

The job is basically unload the totes on the trolley, and merge the totes with the same order numer.   

# Requirment
To determine the staffing lever for each shift to meet the delivery demand. 

# Input:
1. hourly demand in orders from 8am to 8pm.
Conversion from numer of orders to labor hours reqiured.
$$\text{labor_hours} = \text{#orders * avg_totes_per_order * avg_tote_time/3600 }$$
For example:
We have 100 orders for 8am. The avg_totes_per_order is 6 totes, and 
the avg_tote_time is 30 seconds per tote.

The required labor_hours for staging is estimated as:
$100*6*30/3600=5 hours$

So, for 100 orders, we need 5 labor hours to fill.

<!-- # Model -->
<!-- ## Set and parameter -->

<!--   1. $S:$ shift sets which comprised of full time and part time workers. indexed by s. -->

<!--   2. $H:$ 1 to 24 hour, indexed by i,j -->

<!--   3. $length_s$: the length of each shift, such as 8hours, 6hours -->

<!--   4. $\text{shift_map}_{is}$: 0-1 matrix mapping the shift with hours -->

<!--   5. $demand_j$: labor hours demand for each delivery hour -->

<!-- ## Variable -->
<!-- 1. $y_s$: how many staff do we need for each shift. -->

<!-- 2. $x_{ij}$ the number of hours spent on the stagging at hour i for hour j. -->
<!-- This has to be synced with the picking activity.  -->

<!-- ## Objective -->
<!-- Minimizing the total labor hours: -->
<!-- $$\min \sum \limits_{s}^{S} \text{length}_{s} * y_s $$ -->
<!-- ## Constraint -->
<!-- 1. The stagging activity meet the demand.  -->

<!-- $$\sum \limits_{j-4 <= i <=j-1}^{24} x_{ij} = Demand_j,   \forall j \in H$$ -->
<!-- 2. The number of scheduled workers are greater than the sum of each hour's activities.  -->

<!-- $$\sum \limits_{j}^{24} x_{ij}/ \text{efficency} \le  \sum \limits_{s}^{S} shift_{is}*y_{s} , i \in  1 \ldots 24$$ -->

<!-- 3. maintain 70% full time and 30% part time shift -->
<!-- $$  ∑(s \in S|Length(s)≤6) y_s ≤ \text{Ratio_Part_to_Full}*∑(s \in S|length(s)>6)y_s     $$ -->
```{r include=FALSE}
library(tidyverse)
library(ROI)
#library(ROI.plugin.glpk) # Solver or calculator
library(ROI.plugin.cbc)
library(ompr) # the math modeling language
library(ompr.roi)
library(DT)
library(plotly)
library(glue)
```


```{r include=FALSE}
orders_up  <- 150
# orders_low <- 100
# From 1 to 24
#order_demand <- rep(orders_up, 13) # 8am to 8pm 13

# order_demand <- c(59, 59, 49, 56, 100, 59, 99, 59, 69, 54, 50, 50, 50)
 
order_demand <- c(80,80,120,120,120,130,130,130,130,130,110,100,90,30)

# order_demand <-c(46,59,58,75,85,96,54,54,43,48,43,33,13,0)
order_demand <- append(order_demand, c(0,0,0,0,0,0,0),
                               after =0) # 1am to 7am
# order_demand <- append(order_demand, c(0,0,0,0),
#                                after =20) # 9pm to midnight

order_demand <- append(order_demand, c(0,0,0),
                               after =21) # 10pm to midnight

# 
full_shift_set <- matrix(
 c( # 4 hours shift 
        0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #3-6 
        0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-7  
        0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #5-8  
        0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #6-9  
        0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #7-10 
        0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #8-11 
        0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #9-12 
        0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #10-13 
        0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #11-14
        0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0, #12-15
        0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0, #13-16
        0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0, #14-17
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0, #15-18
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0, #16-19
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0, #17-20
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0, #18-21
        

        # 5 hours shift
        0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #3-7
        0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-8    11
        0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #5-9    12
        0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #6-10   13
        0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #7-11   14
        0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #8-12   15
        0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #9-13   17
        0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #10-14  18 
        0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #11-15  19
        0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0, #12-16  20
        0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0, #13-17  21
        0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0, #14-18  22
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0, #15-19  23
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0, #16-20  24
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0, #17-21  
      
       # 6 hours shift 
        0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #3-8
        0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-9   
        0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #5-10  
        0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #6-11  
        0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #7-12  
        0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #8-13  
        0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #9-14  
        0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #10-15  
        0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0,0, #11-16 
        0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0,0, #12-17 
        0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0,0, #13-18 
        0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0,0, #14-19 
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0,0, #15-20 
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,0,0,0, #16-21 
       # 7 hours shift 
        0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #3-9
        0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-10   
        0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #5-11  
        0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #6-12  
        0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #7-13  
        0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #8-14  
        0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #9-15  
        0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0, #10-16  
        0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0,0, #11-17 
        0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0,0, #12-18 
        0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0,0, #13-19 
        0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0,0, #14-20 
        0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,0,0,0, #15-21 
       # 8 hours shift
        0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #3-10
        0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-11   1
        0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #5-12   2
        0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #6-13   3
        0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #7-14   4
        0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #8-15   5
        0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0, #9-16   6
        0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0, #10-17  7
        0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0, #11-18  8
        0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0, #12-19  9
        0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0, #13-20  10
        0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0 #14-21  10
        
      ),ncol = 24,byrow = T)

nshift = nrow(full_shift_set)
shift_length = rowSums(full_shift_set)
```
```{r}
set_ops_time <- function(operation_start_hour){
  
  store_para <- list()
  
  store_para$full_pick_start_hour   = operation_start_hour
  store_para$full_pick_end_hour6    = 16
  store_para$full_pick_end_hour7    = 15
  store_para$full_pick_end_hour8    = 14
  
  
  store_para$full_shift_len6        = 6
  store_para$full_shift_len7        = 7
  store_para$full_shift_len8        = 8
  
  store_para$part_pick_start_hour   = operation_start_hour
  store_para$part_pick_end_hour4    = 18
  store_para$part_pick_end_hour5    = 17
  
  
  store_para$part_shift_len4        = 4
  store_para$part_shift_len5        = 5
  
  return(store_para)
}
  


# store operation list

gen_shifts_matrix <- function(def) {
  f <- function(x, dur) between(1:24, x, x + dur - 1) %>% as.integer()
  full_seq(def$start_range, 1) %>% 
    # {setNames(., sprintf("d%02ds%02d", def$duration, .))} %>% 
    sapply(., f, def$duration) %>% 
    t(.)
}




get_shifts_spec <- function(opt) {
  # Generates a list of shifts with start hour range and duration from
  # a flat file specification with columns names
  list(
    part_time_4 = list(
      start_range = c(opt$part_pick_start_hour, opt$part_pick_end_hour4),
      duration    = opt$part_shift_len4
    ),
    part_time_5 = list(
      start_range = c(opt$part_pick_start_hour, opt$part_pick_end_hour5),
      duration    = opt$part_shift_len5
    ),
    full_time_6  = list(
      start_range = c(opt$full_pick_start_hour, opt$full_pick_end_hour6),
      duration    = opt$full_shift_len6
    ),
    full_time_7  = list(
      start_range = c(opt$full_pick_start_hour, opt$full_pick_end_hour7),
      duration    = opt$full_shift_len7
    ),
    full_time_8  = list(
      start_range = c(opt$full_pick_start_hour, opt$full_pick_end_hour8),
      duration    = opt$full_shift_len8
    )
   
  )
}

store_para <- set_ops_time(3)

full_shift_set <- store_para %>%
  get_shifts_spec(.) %>%
  map(., gen_shifts_matrix) %>%
  reduce(., rbind)


```



```{r include=FALSE}


efficiency = 0.75
Ratio_Full_to_Part = 5.5 
lead_time = 5

Staffing_optimizer  <- function(demand, 
                                efficiency,
                                Ratio_Full_to_Part, 
                                lead_time,
                                time_limit) {


full_time_ind <- which(shift_length > 6)
part_time_ind <- which(shift_length < 6)
# efficiency = 1
  
model <- MIPModel() %>% 
  add_variable(x[i,j], i= 1:24, j = 1:24, type = "continuous",  lb =0) %>% 
  
  add_variable(y[s], s = 1:nshift, type = "integer", lb = 0) %>%
  
  set_objective(sum_expr(y[s]*shift_length[s], 
                         s = 1:nshift ), "min") %>% 
 # picking labor hours should be less than scheduled #picker 
  add_constraint(sum_expr(x[i,j] / efficiency, j =1:24, i >= j - lead_time, i < j-time_limit) <= 
                 sum_expr(y[s] * full_shift_set[s,i], s = 1:nshift),
                 i = 1:24) %>% 
 # picking should meet the demand  
  add_constraint(sum_expr(x[i,j], i = 1:24,  i >= j - lead_time, i < j- time_limit) == 
                   demand[j],
                 j = 1:24)  %>% 
  # control the ration of full time 15% and part time 85%
 add_constraint(sum_expr(y[s], s = part_time_ind) >=
                 sum_expr(y[s], s = full_time_ind) * Ratio_Full_to_Part)


result <- solve_model(model, with_ROI(solver = "cbc", max_time = 60))
#result <- solve_model(model, with_ROI(solver = "cbc"))
#result$objective_value
return(result)
}




### run staging model
avg_totes_per_order <- 6
avg_time_per_totes <- 37

Staging_demand <- order_demand * avg_totes_per_order * 
  avg_time_per_totes/3600

staging_result <- Staffing_optimizer(Staging_demand,
                                     efficiency = 0.95,
                                     Ratio_Full_to_Part = 5.5,
                                     lead_time = 5,
                                     time_limit = 1)


### run picking model
order_size <- 40 # average items in an order
pick_rate  <- 58  # average seconds spent on picking 1 item
Picking_demand <- order_demand * order_size * pick_rate / 3600 

picking_result <- Staffing_optimizer(Picking_demand, 
                                     efficiency = 0.95,
                                     Ratio_Full_to_Part = 5.5,
                                     lead_time = 5,
                                     time_limit = 1)



### run destaging model --------------------
# destaging_time_per_order <- 0.17 # 0.17 hour 
# destaging_demand <- order_demand * destaging_time_per_order 


# distribution of 40%, 25%, 15%, 10%, 5%, 5% 
# returns the number of stagers needed for each demand to maintain 5min waiting time
# how many de-stager need for 
destage_5min_service <- matrix(c(
0, 0,
10	,1,
20	,2,
30	,3,
40	,3,
50	,4,
60	,4,
70	,5,
80	,6,
90	,6,
100, 7,
110, 7,
120, 8,
130, 9,
140, 9,
150, 10,
160, 10,
170, 11,
180, 12,
190, 12,
200, 13),
ncol = 2, byrow = T) %>%
  as_tibble()

colnames(destage_5min_service) <- c("order", "staff")

# use the staff as the labor demand 
order_demand_destage <- tibble(order = order_demand) %>% 
                               left_join(destage_5min_service) %>% 
  select(staff) %>% unlist() %>% unname()
  

detage_demand <- tibble(order = round(order_demand+5, -1)) 

destaging_optimizer <- function(demand,
                                Ratio_Full_to_Part){

  full_time_ind <- which(shift_length > 6)
  part_time_ind <- which(shift_length < 6)
  
  Model <- MIPModel() %>% 
    add_variable(y[s], s = 1:nshift, type = "integer", lb = 0) %>% 
    set_objective(sum_expr(y[s] * shift_length[s], s=1:nshift), "min") %>% 
    
    add_constraint(sum_expr(y[s] * full_shift_set[s,i], s = 1:nshift) 
                   >= demand[i], i = 1:24 ) %>% 
    add_constraint(sum_expr(y[s], s = part_time_ind) >=
                   sum_expr(y[s], s = full_time_ind) * Ratio_Full_to_Part)
  
  result <- solve_model(Model, with_ROI(solver = "cbc", max_time = 60))
  return(result)
}


destaging_result <- destaging_optimizer(order_demand_destage,
                                        Ratio_Full_to_Part = 5.5)

Destaging_data <- destaging_result %>% 
  get_solution(y[s]) %>%
  filter(value > 0) 



start <- rep(0, nrow(Destaging_data))
end   <- rep(0, nrow(Destaging_data))
for( i in 1:nrow(Destaging_data)){
  shift_hour_index <- which(full_shift_set[Destaging_data$s[i],] == 1)
  start[i]  = shift_hour_index[1]
  end[i]    = shift_hour_index[length(shift_hour_index)]
}
Destaging_data$start <- start
Destaging_data$end   <- end

Destaging_data$variable <- NULL
Destaging_data$s <- NULL
colnames(Destaging_data) <- c(#'Shift_ind',
                         'N_Staff', "Shift_Start_Time","Shift_End_Time"
)


```






```{r echo=FALSE}
Staging_data <- staging_result %>% 
  get_solution(y[s]) %>%
  filter(value > 0) 

start <- rep(0, nrow(Staging_data))
end   <- rep(0, nrow(Staging_data))
for( i in 1:nrow(Staging_data)){
  shift_hour_index <- which(full_shift_set[Staging_data$s[i],] == 1)
  start[i]  = shift_hour_index[1]
  end[i]    = shift_hour_index[length(shift_hour_index)]
}
Staging_data$start <- start
Staging_data$end   <- end

Staging_data$variable <- NULL
Staging_data$s <- NULL
colnames(Staging_data) <- c(#'Shift_ind',
                         'N_Staff', "Shift_Start_Time","Shift_End_Time"
)


```

## 4/20/2020 example


```{r fig.width= 10,echo=FALSE}
my_theme <- function(){
  theme(plot.title = element_text(hjust = 0.5, face="bold", color="#34495E"),
            axis.title.y = element_text(face="bold", color="#34495E", 
                                        size=10),
            axis.title.x = element_text(face="bold", color="#34495E", 
                                        size=10),
            axis.text.y = element_text(face="bold", color="#993333", 
                                       size=10))
}


my_tibble <- tibble(
  `Hour Of The Day` = as.integer(seq_len(24)),
  `Order Demand` = order_demand,
  `Required Hours` = round(Staging_demand,1),
) 

p <- my_tibble %>% 
ggplot(aes(`Hour Of The Day`, `Order Demand`, fill = `Required Hours`,
           text = paste("Hour: ",`Hour Of The Day`, 
                        "<br />Demand: ",`Order Demand`,  
                        "<br />Req Hrs: ",`Required Hours`
                        ))) +
  geom_bar(stat = "identity") +
  ggtitle("Staging Shift Optimization \n Store ci305") +
  scale_x_continuous(breaks = scales::pretty_breaks(12)) +
  scale_fill_gradient(low = "red", high = "green") +
  my_theme()


ggplotly(p, tooltip = c("text")) 
```





***

### Data

- Belowe is a date of the data displayed in the plot above.

```{r echo=FALSE, fig.width= 10}

display_table <- t(
  my_tibble %>%
  select(2:3)
)

colnames(display_table) <- as.integer(seq_len(24))
 
display_table %>%
  as_tibble(rownames = "Hour") %>%
 datatable(rownames = FALSE, options = list(scrollX = TRUE, searching= FALSE, paging = FALSE, bInfo = FALSE,
                                            class = 'cell-border stripe', columnDefs = list(list(className = 'dt-center', targets = 0:23))))
```






***

### Staging Recommendation

- The graphic below displays number of staging optimization information.

- Hovering over a shift will display information about the shift staging requirements.

***
***

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width= 10}
cols <- RColorBrewer::brewer.pal(length(unique(Staging_data$Shift_Start_Time)), name = 'Set3') 
Staging_data$color <- factor(Staging_data$Shift_Start_Time)

Staging_data$Shift_End_Time <- Staging_data$Shift_End_Time + 1

p <- plot_ly()

f <- list(
  family= "Courier",
  size = 19
)

X <- list(
  title = "Hour of The day",
  titlefont = f,
  showline = T,
  linecolor = "black"
)


Y <-list(
  title = "Shift",
  titlefont = f,
  autotick = F, 
  dtick = c(1,4),
  showline = T,
  linecolor = "black"
)
  
for(i in 1:(nrow(Staging_data))){
  p <- add_trace(p,
                 x = c(Staging_data$Shift_Start_Time[i], Staging_data$Shift_End_Time[i]), 
                 y =c(i),
                 mode = "lines",
                 line = list(color = Staging_data$color[i], width = 20),
                 showlegend = F,
                 hoverinfo = "text",
                 text = paste("Start: ", Staging_data$Shift_Start_Time[i], "<br>",
                              "End: ", Staging_data$Shift_End_Time[i], "<br>",
                              "N_Staff: ", Staging_data$N_Staff[i], "<br>"),
                 evaluate = T
  ) %>%
    layout(title = "Staging Recommendation By Shift", 
           xaxis = X, 
           yaxis = Y
           ) %>%
    config(displayModeBar = F)
    
}

p
```


- Shift 1 represent disctinct start and end times for staging operations for full time staff throughout the day.

- Shift 2 through 6 represent disctinct start and end times for staging operations  for part time staff throughout the day.

- The model currently recommends one staff for the entire day due to low demand.


***
***

### Data 

- Below is a table that contains the recommended number of staff per shift.

```{r echo=FALSE, fig.width= 10}
Staging_data %>%
  select(-color) %>%
  datatable(rownames = FALSE, options = list(scrollX = TRUE, searching= FALSE, paging = FALSE, bInfo = FALSE,
                                            class = 'cell-border stripe', columnDefs = list(list(className = 'dt-center'))))
```





### Picking Recommendation

- The graphic below displays number of picking optimization information

- Hovering over a shift will display information about the shift picking requirements.

***
***


```{r echo=FALSE}
Pickin_data <- picking_result %>% 
  get_solution(y[s]) %>%
  filter(value > 0) 

start <- rep(0, nrow(Pickin_data))
end   <- rep(0, nrow(Pickin_data))
for( i in 1:nrow(Pickin_data)){
  shift_hour_index <- which(full_shift_set[Pickin_data$s[i],] == 1)
  start[i]  = shift_hour_index[1]
  end[i]    = shift_hour_index[length(shift_hour_index)]
}
Pickin_data$start <- start
Pickin_data$end   <- end

Pickin_data$variable <- NULL
Pickin_data$s <- NULL
colnames(Pickin_data) <- c(#'Shift_ind',
                         'N_Staff', "Shift_Start_Time","Shift_End_Time"
)

```



```{r message=FALSE, echo=FALSE, warning=FALSE }
cols <- RColorBrewer::brewer.pal(length(unique(Pickin_data$Shift_Start_Time)), name = 'Set3') 
Pickin_data$color <- factor(Pickin_data$Shift_Start_Time)

Pickin_data$Shift_End_Time <- Pickin_data$Shift_End_Time + 1

p <- plot_ly( hoverinfo = "text")
  
for(i in 1:(nrow(Pickin_data))){
  p <- add_trace(p,
                 x = c(Pickin_data$Shift_Start_Time[i], Pickin_data$Shift_End_Time[i]), 
                 y =c(i),
                 mode = "lines",
                 line = list(color = Pickin_data$color[i], width = 20),
                 showlegend = F,
                 hoverinfo = "text",
                 text = paste("Start: ", Pickin_data$Shift_Start_Time[i], "<br>",
                              "End: ", Pickin_data$Shift_End_Time[i], "<br>",
                              "Staff: ", Pickin_data$N_Staff[i], "<br>"),
                 evaluate = T
  ) %>%
    layout(title = "Picking Shift Recommendation", 
           xaxis = X, 
           yaxis = Y,
           hovermode = "X") %>%
    config(displayModeBar = F)
    
}

p
```



- Shift 1 through represent 4 disctinct start and end times for picking operations throughout the day for part time employees.

- Each shift contains information about number of associated recommended for manning picking operations with the given shift period.

- There are several time intervals where the shifts overlap. These are areas where the model suggests multiple picker from different shifts working simulteniously to efficiently meet order demands. 

***
***

### Data

```{r, echo=FALSE}
Pickin_data %>% 
  select(-color) %>%
  datatable(rownames = FALSE, options = list(scrollX = TRUE, searching= FALSE, paging = FALSE, bInfo = FALSE,
                                            class = 'cell-border stripe', columnDefs = list(list(className = 'dt-center'))))
```


```{r echo=FALSE}
picking_activitiy <- picking_result %>% 
  get_solution(x[i,j]) %>%
  filter(value > 0) 
picking_activitiy$value <- round(picking_activitiy$value,2)

# knitr::kable(pick_num, "markdown")
# Shift activity tell us what we need to do at each hour either picking or staging.
```


```{r}
output_total <- tibble(
Staff = c(sum(Pickin_data$N_Staff), sum(Staging_data$N_Staff), sum(Destaging_data$N_Staff)),
               Hours =      c(sum(Pickin_data$N_Staff*(Pickin_data$Shift_End_Time-Pickin_data$Shift_Start_Time)),
           sum(Staging_data$N_Staff*(Staging_data$Shift_End_Time - Staging_data$Shift_Start_Time)), 
           sum(Destaging_data$N_Staff*(Destaging_data$Shift_End_Time - Destaging_data$Shift_Start_Time))))

total_staff_hours <- colSums(output_total)
output_total <- rbind(output_total, total_staff_hours)
row.names(output_total) <- c('pick','stage','de-stage', 'total')
knitr::kable(output_total, "markdown")

```

```{r}
library(stringr)





describe_part_full <- function(result){
  # to add the FT/PT with the activity name based on the exsiting result
  pt_ft <- as.character(substitute(result))
  result$Job <- case_when(
    (result$Shift_End_Time - result$Shift_Start_Time) >= 6 ~ str_c( "FT ",
                       word(pt_ft, 1, sep = "\\_",)),
   (result$Shift_End_Time - result$Shift_Start_Time)  < 6 ~ str_c( "PT ",
                       word(pt_ft, 1, sep = "\\_",)),
  )
  return(result)
}


# Staging_data <- describe_part_full(Staging_data)

# breakdown the starting time by pt/ft and start hour

hour_start <- 3
hour_end   <- 21

breakdown_start_time <- function(result){
  # the parameter has to contain column pt/ft description
  result <- result %>% 
    select(N_Staff, Shift_Start_Time, Shift_End_Time, Job) %>% 
    group_by(Job) %>% 
    mutate(Total_Staff = sum(N_Staff),
           Total_Hours = sum(N_Staff *(Shift_End_Time + 1 -Shift_Start_Time)))
  
  # the begin and end of service hour
  operation_hour <- tibble(Shift_Start_Time = seq(hour_start,hour_end))
  
  # map the scheduleing starting hour to the full operation hour 
  breakdown_count <- operation_hour %>% 
    left_join(
      result %>% select(Shift_Start_Time, N_Staff, Job),
      by = "Shift_Start_Time") %>% 
    group_by(Shift_Start_Time, Job) %>%
    summarise(N_Staff = sum(N_Staff)) %>% 
    spread(Shift_Start_Time, N_Staff) %>% 
    filter(Job != "NA") %>% 
    # join the result table to get the total staff and hours
    left_join(distinct(result[c("Job", "Total_Staff",  "Total_Hours")])) %>% 
    # reorder the column
    select(Job, Total_Staff,Total_Hours, everything())
  
  return(breakdown_count)
  
}
 

breakdown_start_table <- map_df(
  list(
  describe_part_full(Pickin_data), 
  describe_part_full(Staging_data),
  describe_part_full(Destaging_data)
  ),
  breakdown_start_time)


options(knitr.kable.NA = '')
knitr::kable(breakdown_start_table, "markdown")
```


```{r}



cumulate_hours <- function(data){
  # data is result of the optimizaton model
  # result <- describe_part_full(data)
  hour  <- hour_start:hour_end
  
  total <- sapply(hour, function(i) 
    sum(data$N_Staff[data$Shift_Start_Time <= i & data$Shift_End_Time >= i]))
  output <- data.frame(hour, total) %>%  spread(hour, total)
  
  return(output)
}

cumulated_table <- map_df(list(
                       Pickin_data,
                       Staging_data,
                       Destaging_data),
                     cumulate_hours)

cumulated_table <- cumulated_table %>% add_column(Job = c("Pick", "Stage", "Destage"), .before = "4")

```
```{r}
pt_ft_start_table <- function(result){
  
    result <- result %>% 
        mutate(Shift_Length = Shift_End_Time - Shift_Start_Time+1)
      
      # the begin and end of service hour
      operation_hour <- tibble(Shift_Start_Time = seq(hour_start,hour_end))
      
      # map the scheduleing starting hour to the full operation hour 
      breakdown_count <- operation_hour %>% 
        left_join(
          result %>% select(Job, Shift_Length, Shift_Start_Time, N_Staff),
          by = "Shift_Start_Time") %>% 
        spread(Shift_Start_Time, N_Staff ) %>% 
        filter(Job != "NA")
  return(result)  
}
  
  

```

