---
title: "Staging Shift Schedule for GPC Ci305"
author: "Shuai Wang & Aaron Makubuya"
date: "4/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem statement
The staging/unstaging work is done by dedicated personnel.

The job is basically unload the totes on the trolley, and merge the totes with the same order numer.   

# Requirment
To determine the staffing lever for each shift to meet the delivery demand. 

# Input:
1. hourly demand in orders from 8am to 8pm.
Conversion from numer of orders to labor hours reqiured.
$$\text{labor_hours} = \text{#orders * avg_totes_per_order * avg_tote_time/3600 }$$
For example:
We have 100 orders for 8am. The avg_totes_per_order is 6 totes, and 
the avg_tote_time is 30 seconds per tote.

The required labor_hours for staging is estimated as:
$100*6*30/3600=5 hours$

So, for 100 orders, we need 5 labor hours to fill.

<!-- # Model -->
<!-- ## Set and parameter -->

<!--   1. $S:$ shift sets which comprised of full time and part time workers. indexed by s. -->

<!--   2. $H:$ 1 to 24 hour, indexed by i,j -->

<!--   3. $length_s$: the length of each shift, such as 8hours, 6hours -->

<!--   4. $\text{shift_map}_{is}$: 0-1 matrix mapping the shift with hours -->

<!--   5. $demand_j$: labor hours demand for each delivery hour -->

<!-- ## Variable -->
<!-- 1. $y_s$: how many staff do we need for each shift. -->

<!-- 2. $x_{ij}$ the number of hours spent on the stagging at hour i for hour j. -->
<!-- This has to be synced with the picking activity.  -->

<!-- ## Objective -->
<!-- Minimizing the total labor hours: -->
<!-- $$\min \sum \limits_{s}^{S} \text{length}_{s} * y_s $$ -->
<!-- ## Constraint -->
<!-- 1. The stagging activity meet the demand.  -->

<!-- $$\sum \limits_{j-4 <= i <=j-1}^{24} x_{ij} = Demand_j,   \forall j \in H$$ -->
<!-- 2. The number of scheduled workers are greater than the sum of each hour's activities.  -->

<!-- $$\sum \limits_{j}^{24} x_{ij}/ \text{efficency} \le  \sum \limits_{s}^{S} shift_{is}*y_{s} , i \in  1 \ldots 24$$ -->

<!-- 3. maintain 70% full time and 30% part time shift -->
<!-- $$  ∑(s \in S|Length(s)≤6) y_s ≤ \text{Ratio_Part_to_Full}*∑(s \in S|length(s)>6)y_s     $$ -->
```{r include=FALSE}
library(tidyverse)
library(ROI)
library(ROI.plugin.glpk) # Solver or calculator
#library(ROI.plugin.cbc)
library(ompr) # the math modeling language
library(ompr.roi)
library(DT)
library(plotly)
library(glue)
```


```{r include=FALSE}
orders_up  <- 150
# orders_low <- 100
# From 1 to 24
# working_hours_demand <- rep(orders_up, 13) # 8am to 8pm 13
# working_hours_demand <- c(20, 20, 30, 40, 50, 55,60, 55,50, 40, 30, 30, 20)

order_demand <- c(17, 16, 21, 25, 26, 34, 38, 35, 33, 38 ,31, 25, 20)


order_demand <- append(order_demand, c(0,0,0,0,0,0,0),
                               after =0) # 1am to 7am
order_demand <- append(order_demand, c(0,0,0,0),
                               after =20) # 9pm to midnight
avg_totes_per_order <- 6
avg_time_per_totes <- 37

Staging_demand <- order_demand * avg_totes_per_order * 
  avg_time_per_totes/3600

# 
full_shift_set <- matrix(
c(
0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-11   1
0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #5-12   2
0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #6-13   3
0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #7-14   4
0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #8-15   5
0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0, #9-16   6
0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0, #10-17  7
0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0,0, #11-18  8
0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0,0, #12-19  9
0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,0,0,0,0, #13-20  10
0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #4-8    11
0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #5-9    12
0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0, #6-10   13
0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0, #7-11   14
0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0, #8-12   15
0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0, #9-13   17
0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0, #10-14  18 
0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0,0, #11-15  19
0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0,0, #12-16  20
0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0,0, #13-17  21
0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0,0, #14-18  22
0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0,0, #15-19  23
1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,0,0,0,0  #16-20  24
),
ncol = 24,byrow = T)

nshift = nrow(full_shift_set)
shift_length = rowSums(full_shift_set)
```



```{r include=FALSE}
Staffing_optimizer  <- function(demand) {

  efficiency = 0.75
  Ratio_Full_to_Part = 3 
  
  full_time_ind <- which(shift_length > 6)
  part_time_ind <- which(shift_length < 6)
  # efficiency = 1
    
  model <- MIPModel() %>% 
    add_variable(x[i,j], i= 1:24, j = 1:24, type = "continuous",  lb =0) %>% 
    
    add_variable(y[s], s = 1:nshift, type = "integer", lb = 0) %>%
    
    set_objective(sum_expr(y[s]*shift_length[s], 
                           s = 1:nshift ), "min") %>% 
   # picking labor hours should be less than scheduled #picker 
    add_constraint(sum_expr(x[i,j] / efficiency, j =1:24, i >= j -4, i < j-1) <= 
                   sum_expr(y[s] * full_shift_set[s,i], s = 1:nshift),
                   i = 1:24) %>% 
   # picking should meet the demand  
    add_constraint(sum_expr(x[i,j], i = 1:24,  i >= j -4, i < j-1) == 
                     demand[j],
                     # demand[j],
                   j = 1:24)  %>% 
  #  # control the ration of full time 70% and part time 30%
   add_constraint(sum_expr(y[s], s = full_time_ind) >=
                   sum_expr(y[s], s = part_time_ind) * Ratio_Full_to_Part)
  
  
  result <- solve_model(model, with_ROI(solver = "glpk", verbose = TRUE))
#result <- solve_model(model, with_ROI(solver = "cbc"))
#result$objective_value
  return(result)

}

result1 <- Staffing_optimizer(Staging_demand)
```


```{r echo=FALSE}
Staging_data <- result %>% 
  get_solution(y[s]) %>%
  filter(value > 0) 

start <- rep(0, nrow(Staging_data))
end   <- rep(0, nrow(Staging_data))
for( i in 1:nrow(Staging_data)){
  shift_hour_index <- which(full_shift_set[Staging_data$s[i],] == 1)
  start[i]  = shift_hour_index[1]
  end[i]    = shift_hour_index[length(shift_hour_index)]
}
Staging_data$start <- start
Staging_data$end   <- end

Staging_data$variable <- NULL
Staging_data$s <- NULL
colnames(Staging_data) <- c(#'Shift_ind',
                         'N_Staff', "Shift_Start_Time","Shift_End_Time"
)


```

## 4/10/2020 example


```{r fig.width= 10,echo=FALSE}
my_theme <- function(){
  theme(plot.title = element_text(hjust = 0.5, face="bold", color="#34495E"),
            axis.title.y = element_text(face="bold", color="#34495E", 
                                        size=10),
            axis.title.x = element_text(face="bold", color="#34495E", 
                                        size=10),
            axis.text.y = element_text(face="bold", color="#993333", 
                                       size=10))
}


my_tibble <- tibble(
  `Hour Of The Day` = as.integer(seq_len(24)),
  `Order Demand` = order_demand,
  `Required Hours` = round(Staging_demand,1),
) 

p <- my_tibble %>% 
ggplot(aes(`Hour Of The Day`, `Order Demand`, fill = `Required Hours`,
           text = paste("Hour: ",`Hour Of The Day`, 
                        "<br />Demand: ",`Order Demand`,  
                        "<br />Req Hrs: ",`Required Hours`
                        ))) +
  geom_bar(stat = "identity") +
  ggtitle("Staging Shift Optimization \n Store ci305") +
  scale_x_continuous(breaks = scales::pretty_breaks(12)) +
  scale_fill_gradient(low = "red", high = "green") +
  my_theme()


ggplotly(p, tooltip = c("text")) 
```





***

### Staging Shift Data

- Belowe is a date of the data displayed in the plot above.

```{r echo=FALSE, fig.width= 10}

display_table <- t(
  my_tibble %>%
  select(2:3)
)

colnames(display_table) <- as.integer(seq_len(24))
 
display_table %>%
  as_tibble(rownames = "Hour") %>%
 datatable(rownames = FALSE, options = list(scrollX = TRUE, searching= FALSE, paging = FALSE, bInfo = FALSE,
                                            class = 'cell-border stripe', columnDefs = list(list(className = 'dt-center', targets = 0:23))))
```






****

### Staging Shift Recommendation

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width= 10}
cols <- RColorBrewer::brewer.pal(length(unique(Staging_data$Shift_Start_Time)), name = 'Set3') 
Staging_data$color <- factor(Staging_data$Shift_Start_Time)

p <- plot_ly()

f <- list(
  family= "Courier New, Monospace",
  size = 18,
  color = "#34495E"
)

X <- list(
  title = "Hour of The day",
  titlefont = f
)


Y <-list(
  titile = "Shift",
  titlefont = f
)
  
for(i in 1:(nrow(Staging_data))){
  p <- add_trace(p,
                 x = c(Staging_data$Shift_Start_Time[i], Staging_data$Shift_End_Time[i]), 
                 y =c(i), 
                 mode = "lines",
                 line = list(color = Staging_data$color[i], width = 20),
                 showlegend = F,
                 hoverinfo = "text",
                 text = paste("Start: ", Staging_data$Shift_Start_Time[i], "<br>",
                              "End: ", Staging_data$Shift_End_Time[i], "<br>",
                              "Duration: ", Staging_data$duration[i], "<br>",
                              "N_Staff: ", Staging_data$N_Staff[i], "<br>"),
                 evaluate = T
  ) %>%
    layout(title = "Staging Shift Recommendation", 
           xaxis = X, 
           yaxis = Y
           )
    
}

p
```

***


### Recommended Staff Coverage

- Below is a table that contains the recommended number of staff per shift.

```{r echo=FALSE, fig.width= 10}
Staging_data %>%
  datatable(rownames = FALSE, options = list(scrollX = TRUE, searching= FALSE, paging = FALSE, bInfo = FALSE,
                                            class = 'cell-border stripe', columnDefs = list(list(className = 'dt-center'))))
```




### Picking Recommendation

```{r}
#rm(list = ls(all.names = TRUE))

order_size <- 40 # average items in an order
pick_rate  <- 65  # average seconds spent on picking 1 item
Picking_demand <- order_demand * order_size * pick_rate / 3600 



# Call function below
pickin_opt_data <- Staffing_optimizer(Picking_demand)
```



```{r}

Pickin_data <- pickin_opt_data %>% 
  get_solution(y[s]) %>%
  filter(value > 0) 

start <- rep(0, nrow(Pickin_data))
end   <- rep(0, nrow(Pickin_data))
for( i in 1:nrow(Pickin_data)){
  shift_hour_index <- which(full_shift_set[Pickin_data$s[i],] == 1)
  start[i]  = shift_hour_index[1]
  end[i]    = shift_hour_index[length(shift_hour_index)]
}
Pickin_data$start <- start
Pickin_data$end   <- end

Pickin_data$variable <- NULL
Pickin_data$s <- NULL
colnames(Pickin_data) <- c(#'Shift_ind',
                         'N_Staff', "Shift_Start_Time","Shift_End_Time"
)

```


```{r echo=FALSE}
shitf_activitiy <- pickin_opt_data %>% 
  get_solution(x[i,j]) %>%
  filter(value > 0) 
shitf_activitiy$value <- round(shitf_activitiy$value,2)

# knitr::kable(pick_num, "markdown")
# Shift activity tell us what we need to do at each hour either picking or staging.
```



